Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-06-01 outputs/paper/paper.qmd
Edited typo

## Data
The data utilized throughout this paper was obtained through the City of Toronto’s OpenDataToronto Library [@rOpenDataToronto]. The two different data sets used are: “Elections Voting Locations” [@VotingLocations] and “Elections - Voter Statistics” [@VoterStatistics]. Data was collected and analyzed using the statistical programming software R (R Core Team, 2022), with additional support from from `tidyverse` [@rTidyverse], `ggplot2` [@rGgplot2], `dplyr` [@rDplyr], `readr` [@rReadr], `tibble` [@rTibble], and `janitor` [@rJanitor]. A further discussion of the data collection, cleaning, and analysis process can be found later on in this paper.

>>>>

## Data
The data utilized throughout this paper was obtained through the City of Toronto’s OpenDataToronto Library [@rOpenDataToronto]. The two different data sets used are: “Elections Voting Locations” [@VotingLocations] and “Elections - Voter Statistics” [@VoterStatistics]. Data was collected and analyzed using the statistical programming software R (R Core Team, 2022), with additional support from `tidyverse` [@rTidyverse], `ggplot2` [@rGgplot2], `dplyr` [@rDplyr], `readr` [@rReadr], `tibble` [@rTibble], and `janitor` [@rJanitor]. A further discussion of the data collection, cleaning, and analysis process can be found later on in this paper.
